Global patterns of forest autotrophic carbon fluxes

### 2020-05-05 manuscript/manuscript draft.Rmd
update allocation results
#73

We found little evidence that allocation between fluxes varied substantially with latitude or climate (Fig. S3). Of the 7 FACF ratios regressed against latitude and three climate variables (MAT, MAP, temperature seasonality), there were only four signficant relationships, all with $R^2 \le 0.2$ (Fig. S3). Specifically, the proportion of NPP allocated to $ANPP_{foliage}$ increased weakly with MAT ($R^2=0.20$), and the proportion of $NPP$ allocated aboveground ($ANPP$) decreased weakly with latitude ($R^2=0.11$) and temperature seasonality ($R^2=0.17$), while increasing with MAT ($R^2=0.11$).  There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.

@@

*reworking the above paragraph:*
We show that FACF are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple FACF varies little with respect to climate along a tropical elevational gradient [@malhi_variation_2017], 
but contrasts with observed variation in allocation along gradients of elevation [@moser_elevation_2011] and water availability [@newman_above-_2006]
- @gill_belowground_2016 ?
- (others in list below?)
Several trends in allocation--or lack thereof--warrant discussion.
1. CUE
2. We found a slight tendency for warmer sites to have higher aboveground allocation (Fig. S3). This is consistent with:
- [@hofhansl_new_2015] (**verify**) 
- Chen et al. 2019 (doi: 10.1111/ele.13193) - find lower partitioning belowground at higher productivity (fine root NPP scales against ANPP_foliage with a slope of ~ 0.8)
- @gill_belowground_2016
- @litton_carbon_2007 - (verify)

>>>>

We found little evidence that allocation between fluxes varied substantially with latitude or climate (Fig. S3). Of the 7 FACF ratios regressed against latitude and three climate variables (MAT, MAP, temperature seasonality), there were only five signficant relationships, all with $R^2 \le 0.4$ (Fig. S3). Specifically, the proportion of NPP allocated to $ANPP_{foliage}$ decreased with latitude ($R^2=0.32$) and increased with MAT ($R^2=0.37$), and the proportion of $NPP$ allocated aboveground ($ANPP$) decreased weakly with latitude ($R^2=0.11$) and temperature seasonality ($R^2=0.17$), while increasing with MAT ($R^2=0.11$).  There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.

@@

*reworking the above paragraph:*
We show that FACF are broadly consistent in their responses to climate drivers on the global scale, with at most modest trends in C allocation among the variable pairs tested (Figs. 2, S3). 
This parallels the observation that C allocation across multiple FACF varies little with respect to climate along a tropical elevational gradient [@malhi_variation_2017], 
but contrasts with observed variation in allocation along gradients of elevation [@moser_elevation_2011] 
- @gill_belowground_2016 ?
- (others in list below?)
Several trends in allocation--or lack thereof--warrant discussion.
1. CUE
2. We found a slight tendency for warmer sites to have higher aboveground allocation (Fig. S3). This is consistent with:
- [@hofhansl_new_2015] (**verify**) 
- @moser_elevation_2011 (tropical elevation gradient)
- Chen et al. 2019 (doi: 10.1111/ele.13193) - find lower partitioning belowground at higher productivity (fine root NPP scales against ANPP_foliage with a slope of ~ 0.8)
- @gill_belowground_2016
- @litton_carbon_2007 - (verify)
